\LARGE \bf Reactive Trajectory Planning and Tracking for Pedestrian-Aware Autonomous Driving in Urban Environments

### 2016-04-14 root.tex
removed pdf, and made some reviewer changes

\begin{figure}[tb]
  \centering
  \includegraphics[width=0.7\columnwidth]{graphics/its_car.png}
  \caption{
    Showing car used in our experiments.
  }
  \label{fig:addreact}
\end{figure}

@@

Pedestrian Detection is performed via a camera and LiDAR system based on \cite{Gepperth2013,Gepperth2014}.
The pedestrian detector outputs a bounding box for each pedestrian as shown in Figure \ref{fig:ped}.
The pedestrian position is computed in the vehicle body frame, and subsequently transformed to the global frame to be related to the planned path.

@@

Path Manager performs trajectory planning over a sliding window within the full path with the sliding window moving with the vehicle.
It breaks the path into sub-paths at each stop location which is known a priori, as shown in Fig. \ref{fig:subpathdivision}, and calls the Trajectory Planner for each sub-path in the path.

@@

This profile, with $\Delta t_i$ as shown in Figure \ref{fig:full7phasespec}, is always attempted first.
All time steps have a single solution, enabled by the fact that the initial and end conditions are known, and the two peak accelerations and two jerk magnitudes are provided as configuration parameters.
In the case where $\Delta t_2$ or $\Delta t_6$ are negative, accel-jerk tuning must be employed.
In the instance where $\Delta t_4$ is negative, the total segment length $L$ is too short to reach top speed of $v_m$, so a 6-phase profile must be used.

@@

In the case mentioned above, the speed limit is too high for a solution to exist for a 7-phase profile.
The middle travel period $\Delta t_4$ is removed, so that the vehicle increases speed and then immediately decreases speed. 
The peak speed, in this case, has a solution that cannot be manipulated directly.
Without this known value, the problem becomes under-defined, so $\Delta t_2$ and $\Delta t_5$ each have two solutions: one negative and one positive.
The positive solution is chosen.
In the case where both solutions are negative, accel-jerk tuning is attempted. 
Should that yield no positive time intervals, one of the two 4-phase profiles then becomes appropriate, since $L$ is not large enough to accommodate accelerating past the end speed.
If $v_i > v_f$, then a reversed 4-phase profile is attempted.
However, if $v_i > v_f$, then a regular 4-phase profile is attempted.

@@

When $v_i < v_m \simeq v_f$, the vehicle should increase speed, then maintain that speed for the distance remaining in the segment.

@@

When $v_i \simeq v_m > v_f$, it would be nonsensical to immediately brake.
The initial speed is maintained for a period before applying the brakes.

@@

A change from one speed to another.
All of the above profiles are composed of some combination of a 3 phase profile and a $j = 0$ phase.
This presents a difficulty in that either $L$ or $v_f$ may be enforced, but not both (there is no solution to enforce both).
As such, this profile is chosen only for a segment in which it is impossible to completely arrive at the end speed given the initial conditions.
When these discrepancies in the feasible $v_f$ for a segment arise, the corresponding value in $v_p$ is updated so that the new conditions may be accounted for in the subsequent segment.

@@

To decide which profile to employ, a cascade approach is used.
Analytic values of time intervals are evaluated for each profile by plugging in new values of $\mathbf{a}_m$ and $\mathbf{j}_m$ until all time intervals are positive and real.
The order in which they are attempted is: 7 $\rightarrow$ 6 $\rightarrow$ 4 / 4R $\rightarrow$ 3.
Each is described below.

@@

>>>>

\begin{figure}[tb]
  \centering
  \includegraphics[width=0.7\columnwidth]{graphics/its_car.png}
  \caption{
    Showing car used in our experiments.
  }
  \label{fig:car}
\end{figure}

@@

Pedestrian Detection is performed via a camera and LiDAR system based on \cite{Gepperth2013,Gepperth2014}.
The pedestrian detector outputs a bounding box for each pedestrian as shown in Figure \ref{fig:ped}.
The pedestrian position is computed in the vehicle body frame, and subsequently transformed to the global frame to be related to the planned path.
Pedestrian detection algorithms are still in heavy development.
In order to make the algorithm robust to detection errors, it is designed under the assumption that pedestrian trajectory estimates and predictions are unavailable.
Furthermore, it is assumed that no unique identifier is available to differentiate one pedestrian from the other in a single epoch, or to correlate the same pedestrian between epochs.

@@

The Path Manager performs trajectory planning over a sliding window within the full path with the sliding window moving with the vehicle.
As shown in Fig. \ref{fig:addreact}, a Path Planner passes paths into it as a 2D linestring.
It then breaks the path into sub-paths at each stop location which is known a priori, as shown in Fig. \ref{fig:subpathdivision}, and calls the Trajectory Planner for each sub-path in the path.

@@

This profile, with $\Delta t_i$ as shown in Figure \ref{fig:full7phasespec}, is always attempted first.
All time steps have a single solution, enabled by the fact that the initial and end conditions are known, and the two peak accelerations and two jerk magnitudes are provided as configuration parameters.
In the case where $\Delta t_2$ or $\Delta t_6$ are negative, accel-jerk tuning must be employed.
The 7-phase profile can be expressed as $( j_1 > 0 , j_2 = 0 , j_3 < 0 , j_4 = 0 , j_5 < 0 , j_6 = 0 , j_7 > 0 )$.
In the instance where $\Delta t_4$ is negative, the total segment length $L$ is too short to reach top speed of $v_m$, so a 6-phase profile must be used.

@@

In the case mentioned above, the speed limit is too high for a solution to exist for a 7-phase profile.
The middle travel period $\Delta t_4$ is removed, so that the vehicle increases speed and then immediately decreases speed. 
The peak speed, in this case, has a solution that cannot be manipulated directly.
Without this known value, the problem becomes under-defined, so $\Delta t_2$ and $\Delta t_5$ each have two solutions: one negative and one positive.
The positive solution is chosen.
In the case where both solutions are negative, accel-jerk tuning is attempted. 
The 6-phase profile can be expressed as $( j_1 > 0 , j_2 = 0 , j_3 < 0 , j_4 < 0 , j_5 = 0 , j_6 > 0 )$
Should that yield no positive time intervals, one of the two 4-phase profiles then becomes appropriate, since $L$ is not large enough to accommodate accelerating past the end speed.
If $v_i > v_f$, then a reversed 4-phase profile is attempted.
However, if $v_i > v_f$, then a regular 4-phase profile is attempted.

@@

When $v_i < v_m \simeq v_f$, the vehicle should increase speed, then maintain that speed for the distance remaining in the segment.
The 4-phase profile can be expressed as $( j_1 > 0, j_2 = 0 , j_3 < 0, j_4 = 0 )$

@@

When $v_i \simeq v_m > v_f$, it would be nonsensical to immediately brake.
The initial speed is maintained for a period before applying the brakes.
The reversed 4-phase profile can be expressed as $( j_1 = 0, j_2 < 0, j_3 = 0 , j_4 > 0 )$

@@

A change from one speed to another.
All of the above profiles are composed of some combination of a 3 phase profile and a $j = 0$ phase.
This presents a difficulty in that either $L$ or $v_f$ may be enforced, but not both (there is no solution to enforce both).
As such, this profile is chosen only for a segment in which it is impossible to completely arrive at the end speed given the initial conditions.
When these discrepancies in the feasible $v_f$ for a segment arise, the corresponding value in $v_p$ is updated so that the new conditions may be accounted for in the subsequent segment.
The 3-phase profile can be expressed as $(j_1 \pm 0 , j_2 = 0, j_3 \mp 0 )$

@@

To decide which profile to employ, a cascade approach is used.
Analytic values of time intervals are evaluated for each profile by plugging in new values of $\mathbf{a}_m$ and $\mathbf{j}_m$ until all time intervals are positive and real.
The order in which they are attempted is: 7 $\rightarrow$ 6 $\rightarrow$ 4 / 4R $\rightarrow$ 3.
Each has been described above.
The routines for fitting a profile to a given $\mathbf{b}, \mathbf{a}_m, \mathbf{j}_m$ to a segment using this cascade approach is referred to as a ``jerk library''.

@@

\textbf{emphasize limited knowledge of pedestrians as a strength}
